---
title: "Data Preppin 2019 Week 8"
author: "David Jackson"
date: "11/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(readxl)
library(writexl)
```

## C&BS Co: accounting for slippery thieves

As we saw last week, Profits are rolling in nicely from Chin & Beard Suds Co. but all is not perfect at the company. Recently our Suds shops have been the victim of a number of thefts. Thankfully our systems allow our stores to record the thefts, when the theft occurred and when we adjusted the inventory to reflect the reduced amounts.

* Input data from both sheets
* Update Store IDs to use the Store Names
* Clean up the Product Type to just return two products types: Bar and Liquid
* Measure the difference in days between when the theft occurred  and when the stock was updated
* Measure the variance in stolen stock and inventory adjustment 

### Input data from both sheets


```{r}
rm(list=ls())
branch <- read_excel("./Data/2019Week8Input.xlsx",sheet = "Branch") %>% clean_names()
theft <- read_excel("./Data/2019Week8Input.xlsx",sheet = "Theft") %>%
  clean_names()

```

### Update Store IDs to use the Store Names

```{r}
branch_name <- branch %>% left_join(theft) %>% select(-store_id) %>% drop_na()


```

### Clean up the Product Type to just return two products types: Bar and Liquid

```{r}

branch_name$type <- ifelse(branch_name$type =="Luquid","Liquid",branch_name$type)
branch_name$type <- ifelse(branch_name$type =="Bar","Soap Bar",branch_name$type)
```

### Item Stolen the Most

```{r}
branch_name %>% filter(action == "Theft") %>% count(type,sort =T) %>%
  ggplot(aes(x=type,n)) + geom_col() + labs(title = "Number of Times Product was Stolen by Type",x="Product Type",y="Number of Timse Product was Stolen")
```

```{r}
branch_name %>% filter(action == "Theft") %>% group_by(type) %>% 
  summarise(total_thefts = sum(quantity)) %>%
  ggplot(aes(x=type,total_thefts)) + geom_col() + labs(title = "Quantity by Soap Type ",x="Soap Type",y="Quantity Stolen")
```

```{r}
branch_name %>% count(branch,action) %>% arrange(branch,action)
branch_name %>% count(branch,action) %>% arrange(branch,action) %>%
  ggplot() + geom_col(aes(x=action,y=n)) + facet_wrap(~branch)
```

#### Measure the variance in stolen stock and inventory adjustment

```{r}
branch_name %>% group_by(branch,type) %>%
  summarise( variance = sum(quantity)) %>%
  ggplot() + geom_col(aes(x=branch,y=variance)) + facet_wrap(~type)
```

### Requirement

```{r}
branch_distinct <- branch_name %>% select(branch,crime_ref_number) %>% distinct()

```
```{r}
branchtheft <- left_join(branch_distinct,theft) 
branchtheft$date <- as.Date(branchtheft$date)
  
```
```{r}
write_xlsx(branchtheft,"./branchtheft.xlsx")
```


