---
title: 'Week 5: Balances, statements, and complaints'
author: "David Jackson"
date: "11/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)
library(readxl)
```

## Balances, statements, and complaints

*Requirements:*

* Input data set
* Create a date per day
* Determine how the customer contacted the company
* Create a separate column for the Policy Number
* Remove contacts that don't have a Policy Number
* Identify whether the contact was about a balance check, getting a statement or raising a complaint (it's all our boss cares about)
* Get rid of unrequired columns

*Output:*

* 15 Rows (16 including the column)
* 6 Columns
* One row per day, per customer and policy

### Read in Excel Data

```{r}
rm(list=ls())
cust_service <- read_excel("./Data/2019Week-05.xlsx")
```
```{r}

cust_service<- cust_service %>% mutate(policy = str_extract(Notes, "#[0-9]+")) %>% drop_na()
```

###  Pull Out Contact Method


```{r}
cust_service<- cust_service %>% mutate(Contact = str_extract(Notes, "Called|Email|")) 
```

## Reason for Contact

```{r}
cust_service <- cust_service %>% mutate(reason = str_extract(Notes, "[Bb]alance|[Ss]tatement|[Cc]omplain|[Aa]ddress|[Nn]ew|[Pp]ostcode")) 
```

### Final Solution

```{r}
cust_service <- cust_service %>% janitor::clean_names()
cust_service <- cust_service %>% select(date,customer_id,policy,reason) 
  
```
```{r}
write.csv(cust_service,file = "customers.csv",row.names = F)
```
```{r}
customer_final <- cust_service %>% dplyr::mutate(filler = rep(1)) %>% tidyr::pivot_wider(names_from = reason, values_from = filler, values_fill = 0)
```


