---
title: "Preppin Data 2019 Week 2"
author: "David Jackson"
date: "10/28/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,error = FALSE,message = FALSE)
library(tidyverse)
library(scales)
library(janitor)
library(lubridate)
```

## Next Weeks Weather

 So you survived week one (note: if you haven’t completed week one - go back and give it a go as we will be layering the techniques over time)... well done and let’s kick this up a notch. 

This week’s challenge uses a few of Jonathan’s and my favourite Tableau Prep features. Prep has a load of great features built in to the menus so let’s see which of them you can use to save you lots of fiddly calculations. 

 So what’s the data? We need you decide where you are going to in the UK; London or Edinburgh, purely based on the weather (every Brit’s favourite subject).

## Requirements for this week:

* **Get rid of those nicely formatted titles - no-one is viewing this in Excel! (sorry Excel fans)
* ** Make sure you get all the data in the Excel sheet loaded in to Prep
*  ** Clean up the City names to create two cities in one column (London and Edinburgh)
* Pivot the data to give a measure per column for the four metrics in the data set
* Output the data to csv


## Read Weather For London and Edinburgh

```{r}
rm(list=ls())
weather <- readxl::read_excel("./Data/Week 2019Week-02.xlsx")
weather <- janitor::clean_names(weather) %>%
  select(city,date,metric:value)
```


## Convert to Piviot Wider with meterics being Columns

```{r}
weather_wider <-weather %>% pivot_wider(names_from =metric,values_from = value) %>% janitor::clean_names()

head(weather_wider) 
```

### Descriptive Statistics

```{r}
weather$metric <- as.factor(weather$metric)
weather$city <- as.factor(weather$city)
weather$measure <- as.factor(weather$measure)
summary(weather)
```

### Plot of Daily Min/Max Temps by Date

```{r}
weather %>% filter(measure =="Celsius") %>%
  ggplot(aes(x=date,y=value,group =metric,col=metric)) + 
  geom_line() + labs(title = "Min/Max Tempatures by Date")
```

### Plot of Daily Min/Max Temps by City and Dates

```{r}
weather %>% filter(measure =="Celsius") %>%
  ggplot(aes(x=date,y=value,group =metric,col=metric)) + 
  geom_line() + labs(title = "Min/Max Temperatures by City and Date",
                     x="Date",y="Temperature(Celsius)") +
  facet_wrap(~city)
```

### Plot of Daily Precipitation by Date

```{r}
weather %>% filter(measure =="mm") %>%
  ggplot(aes(x=date,y=value,group =metric,col=metric)) + 
  geom_line() + labs(title = "Precipitation by Date",x="Date",y="Precipitation (Millimetres)")
```

### Plot of  Precipitation  City and Dates

```{r}
weather %>% filter(measure == "mm") %>%
  ggplot(aes(x=date,y=value,group =metric,fill=metric)) + 
  geom_area() + labs(title = " Precipitation by City and Date",
                    x="Date",y="Precipitation(Millimetres)") +
  facet_wrap(~city)
```


### Plot of Wind Speed by Date

```{r}
weather %>% filter(measure =="mph") %>%
  ggplot(aes(x=date,y=value,group =metric,col=metric)) + 
  geom_line() + labs(title = "Wind Speed by Date",x="Date",y="Wind Speed (MPH)")
```

### Plot of  Wind Speed by  City and Dates

```{r}
weather %>% filter(measure == "mph") %>%
  ggplot(aes(x=date,y=value,group =metric,fill=metric)) + 
  geom_area() + labs(title = " Wind Speed by City and Date",
                    x="Date",y="Wind Speed (MPH)") +
  facet_wrap(~city)
```
