---
title: "Data Preppin Week 1"
author: "David Jackson"
date: "10/27/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,error = FALSE,message = FALSE)
library(tidyverse)
library(scales)
library(janitor)
library(readxl)
library(timetk)
```

## Welcome to your first Preppin' Data challenge.

### Requirements

* ** Make a date that will work in Tableau Desktop
* **Work out the total car sales per month / per car dealership
* Retain the car sales per colour columns
* Export the file 
* Due to the way Tableau Prep works, your output:
* Might not have the same row or column order as our output
* Will have the same number of columns (7)
* Will have the same number of rows (48)

```{r}
rm(list=ls())
car_sales <- read_excel("./Data/2019Week-01.xlsx")
car_sales <- remove_empty(car_sales,which = c("rows","cols"))
car_sales <- clean_names(car_sales)
```

### Calculate Monthly Salse by Dealer

```{r}
car_sales %>% group_by(dealership) %>%
  summarise_by_time(.date_var = date,.by ="month",value = sum(total_cars_sold))
```

```{r}
cars_color <- car_sales %>% select(dealership,date,when_sold_month,when_sold_year,red_cars:blue_cars) %>% pivot_longer(cols=red_cars:blue_cars,names_to = "Auto",values_to = "Total_sold")
```

### Total Sales by Date

```{r}
car_sales %>% group_by(date) %>%
    summarise(total_sales = sum(total_cars_sold)) %>%
  ggplot(aes(x=date,y=total_sales)) + geom_line() +
  labs(title = "Total Cars Sales by Date",y="Quantity Sold") +
  scale_y_continuous(labels = comma_format())
```

### Total Car Sales by Month

```{r}
car_sales %>% group_by(date) %>%
  summarise_by_time(.date_var = date,.by ="month",value = sum(total_cars_sold)) %>% 
  ggplot(aes(x=date,y=value)) + geom_col()
```

### Total Quantity Sold by Colour

```{r}
cars_color %>% group_by(Auto,when_sold_year) %>% 
  summarise(total_colour = sum(Total_sold)) %>%
  ggplot(aes(x=reorder(Auto,total_colour),y=total_colour,fill=Auto)) + geom_col() + facet_wrap(~when_sold_year) +
  theme(axis.text.x=element_blank()) +
  labs(title = "Quantity Sold by Year and Colour",
       y="Total Quantity Sold",x="")
```

## Analysis by Car Dealership

```{r}
car_sales %>% ggplot(aes(x=date,y=total_cars_sold,col=dealership,group = dealership),lwd = 1) +
  geom_line() + labs(title = "Total Cars Sold by Dealership",
                    x="Date", y="Quantity Sold")
```

### Dealership / Autos Sold by Colour

```{r}
cars_color %>% group_by(dealership,Auto) %>%
  summarise_by_time(.date_var = date,.by ="month",value = sum(Total_sold)) %>% ggplot(aes(x=date,y=value,fill=Auto)) + geom_col() +
  facet_wrap(~dealership,ncol=1) +
  labs(title = "Sales by Dearlership and  Auto Color",x="Month Sold",
       y="Quantity Sold") +  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
cars_color %>% group_by(dealership,Auto) %>%
  summarise_by_time(.date_var = date,.by ="quarter",value = sum(Total_sold)) %>% ggplot(aes(x=date,y=value,fill=dealership)) + geom_col(stat = "identity", position = 'dodge') + facet_wrap(~Auto,ncol=1) +
  labs(title = "Car Sales By Quarter",y="Quantity Sold",x="Quarte Sold")
```

