---
title: 'Preppin Data: 2019 Week 4'
author: "David Jackson"
date: "11/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,error=FALSE,message = FALSE)
library(tidyverse)
library(lubridate)
library(readxl)
library(janitor)
library(scales)
library(tidyr)
```

# San Antonio Spurs

* Hi Points = Most points scored by a single player during the game
* Hi Rebounds = Most times a player has recovered possession * after a missed shot
* Hi Assists = Most times a player has passed the ball to another player who then scored.


We have given you data just about Carl's favourite team, the San Antonio Spurs. You will obviously need to clean-up the data, but can then use some other functions in Prep Builder to help you answer the following questions.

1. In games won by the Spurs, which player most often scores the most points?
2. In games lost by the Spurs, which player most often scores the most points?
3. What combination of players scores the most points, rebounds and assists the most frequently?
4. Which player is the second most frequent at gaining the most assists in a game?
5. With the answer to Q4, where do all these games happen: Home or Away?
6. Which player scored the most points in games in October 2018 the most frequently?


## Requirements:

Import the file
Fix some date issues!
Split the "Hi-" categories up so player and value is separate
Determine whether each game was played by the Spurs: Home or Away 
Determine whether the Spurs won or lost each game
Get rid of unrequired columns

### Read In Data and Example Output
#### Answer Sheet

```{r}
rm(list=ls())
answer_sheet <- read_csv("./Data/2019Week04- Output.csv") %>%
  janitor::clean_names()
```

### NBA Data Cleaning

```{r}
raw_data <- read_excel("./Data/2019Week-04.xlsx") %>% 
  janitor::clean_names()
raw_data$opponent <- gsub("vs","1",raw_data$opponent)
raw_data$opponent <- gsub("@","0",raw_data$opponent)
raw_data$opponent <- gsub(" ","_",raw_data$opponent)
raw_data$w_l <- gsub("_","-",raw_data$w_l)
raw_data$X <- parse_number(raw_data$opponent)
raw_data$home_or_away <- ifelse(raw_data$X ==1,"Home","Away")
raw_data$win_or_loss <- substr(raw_data$result,1,1)

raw_data <- raw_data %>% mutate(opponent_clean = str_extract(opponent, "[A-Za-z]+"))

```

```{r}
raw_data <-  separate(raw_data,w_l, c("wins","loss"),sep = "-")
```


#### Pull out Player Name and Points from HI Point Column

```{r}
raw_data <- raw_data %>% mutate(hi_points_player = str_extract(hi_points, "[A-Za-z]+"))

raw_data$hi_points_value <- parse_number(raw_data$hi_points)
raw_data %>% count(hi_points_player,sort =TRUE) %>%
  ggplot() + geom_col(aes(x=reorder(hi_points_player,n),y=n)) +
  labs(title = "Leading Scorer",x="Player's Name",y="Number of Game as Leading scorer")
```

#### Pull out Player Name and Points from HI Rebounds Column

```{r}
raw_data <- raw_data %>% mutate(hi_rebounds_player = str_extract(hi_rebounds, "[A-Za-z]+"))

raw_data$hi_rebounds_value <- parse_number(raw_data$hi_rebounds)

raw_data %>% count(hi_rebounds_player,sort =TRUE) %>%
  ggplot() + geom_col(aes(x=reorder(hi_rebounds_player,n),y=n)) +
  labs(title = "Player with Most Rebounds(per Game)",x="Player's Name",y="Number of Game as Leading Rebounds")
```

#### Pull out Player Name and Points from HI Assist Column

```{r}
raw_data <- raw_data %>% mutate(hi_assist_player = str_extract(hi_assists, "[A-Za-z]+"))

raw_data$hi_assist_value <- parse_number(raw_data$hi_assists)

  raw_data %>% count(hi_assist_player,sort =TRUE) %>%
  ggplot() + geom_col(aes(x=reorder(hi_assist_player,n),y=n)) +
  labs(title = "Player with Most Assist(per Game)",x="Player's Name",y="Number of Game as Leading Assist")
  
```

#### Semi Final Output

```{r}
cleaned_data <- raw_data %>% select(date,opponent_clean,wins,loss,hi_assist_player,
                                     hi_assist_value,hi_rebounds_player,
                                     hi_rebounds_value,hi_points_player,
                                     hi_points_value,win_or_loss,
                                     home_or_away,result)
cleaned_data$hi_assist_player <- as.factor(cleaned_data$hi_assist_player)
cleaned_data$hi_rebounds_player <- as.factor(cleaned_data$hi_rebounds_player)
cleaned_data$hi_points_player <- as.factor(cleaned_data$hi_points_player)
```

## Dlookr Table Summary

```{r}
cleaned_data %>% dlookr::diagnose_numeric() %>% flextable::flextable()
```

### Count the number of Wins/Losses by Opponent

```{r}
cleaned_data %>% count(opponent_clean,win_or_loss,sort = T) %>%
  ggplot() + 
  geom_col(aes(x=opponent_clean,y=n,fill=win_or_loss)) +
  theme(axis.text.x = element_text(angle = 90))
  
```

### In games won by the Spurs, which player most often scores the most points?

```{r}
cleaned_data %>% filter(win_or_loss =="W") %>%
  group_by(hi_points_player) %>% 
  summarise(Count = n()) %>%
  ggplot(aes(x=reorder(hi_points_player,Count),y=Count)) +
  geom_col() + labs(title = "Player With Most Hi Point Games When Game is won")
```

### In games lost by the Spurs, which player most often scores the most points?

```{r}
cleaned_data %>% filter(win_or_loss =="L") %>%
  group_by(hi_points_player) %>% 
  summarise(Count = n()) %>%
  ggplot(aes(x=reorder(hi_points_player,Count),y=Count)) +
  geom_col() + labs(title = "Player With Most Hi Point Games When Game is Lost",x="Hi Scorer Player")
```

### 3. What combination of players scores the most points, rebounds and assists the most frequently?

```{r}

```

### 4. Which player is the second most frequent at gaining the most assists in a game?

```{r}
cleaned_data %>% count(hi_assist_player,sort = T) %>%
  ggplot(aes(x=reorder(hi_assist_player,n),n)) + geom_col(aes(fill=hi_assist_player)) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  labs(title ="Players with the Most Assist",
       x="Players",y="Number of Games")

```

### 5. With the answer to Q4, where do all these games happen: Home or Away?

```{r}
cleaned_data %>% count(hi_assist_player,home_or_away,sort = T) %>%
  ggplot(aes(x=reorder(hi_assist_player,n),n)) + geom_col(aes(fill=hi_assist_player)) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  labs(title ="Players with the Most Assist",
       x="Players",y="Number of Games") +
  facet_wrap(~home_or_away)

```


### 6. Which player scored the most points in games in October 2019 the most frequently?

```{r}
cleaned_data %>% filter(date >="2019-10-01" & date <="2019-10-31") %>%
  count(hi_points_player,sort =T) %>%
  ggplot(aes(x=hi_points_player,y=n)) + geom_col() +
  labs(title = "Players with the Most Hi Point Games in Oct. 2019",
       x = "Hi Point Player",y="Number of Times")
```



